Comparison of Analytical and Artificial Neural Network models in predicting hot deformation behavior of AISI P20

### 2022-11-25 Article.tex
Small corrections to main Article

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{\emph{i.e.}\@\xspace}
\DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\AARE}{\text{E}_\text{AAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}

@@

The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
This method allows obtaining one after the other the 5 parameters in the order $A$, $B$, $n$, $C$ and $m$.
Thus, according to our experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143$~MPa.
For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
Thus, here, $B=21.816$~MPa and $n=0.0746$.
Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.3404$.
Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.7057$.
All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.

\begin{table}[h!]
\centering
\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
\begin{tabular}{ccccc}
	\hline
	$A~(\text{MPa})$ & $B~(\text{MPa})$ &   $n$    &   $C$    &   $m$    \\
	   $13.5143$     &     $21.816$     & $0.0746$ & $0.3404$ & $0.7057$ \\ \hline
\end{tabular}
\label{tab:JC}
\end{table}

@@

The accuracy and predictive ability of the models are usually assessed by certain coefficients such as the Mean Absolute Relative Error ($\AARE$) defined by Equation (\ref{eq:AARE}):
\begin{equation}
\AARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the Root Mean Square Error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
\begin{equation}
\RMSE (\text{MPa}) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value and $\sigma_i^p$ is the predicted value using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
For the JC model, $\AARE=14.05~\%$ and $\RMSE=12.00~\text{MPa}$.
As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure in our case of study because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
Therefore, as a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction we avoided its use in our analysis.

@@

By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$.
The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively.
Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right),
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$.
Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
The parameters of MZA model are given in Table \ref{tab:MZA} while its prediction are plotted in Figure \ref{fig:CompExp-MZA-6}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{ccccccc}
	\hline
	  $C_1$   &   $C_2$   &         $C_3$          &         $C_4$          &  $C_5$   &         $C_6$         &   $n$    \\
	$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$ \\ \hline
\end{tabular}
\label{tab:MZA}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:CompExp-MZA-6}
\end{figure}
It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\text{MPa}$, this shows an overall worse performance than the JC model as reported in \cite{TizeMha-2022}.

@@

The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\text{MPa}$.
It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1~\ps$.
This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate.
The DRX phenomena cannot be reproduced by this type of model.

@@

Figure \ref{fig:CompExp-AR-6} shows the comparison of the values predicted by the Arrhenius model and the experimental values.
The difference between the experimental and predicted values is small.
But for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is not able to predict the softening.
For the AR model, $\AARE=3.56~\%$ and $\RMSE=2.18~\text{MPa}$.

@@

Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:CompExp-PTM-6}.
The PTM model is suitable to describe the ﬂow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction is not quite good.
The deviation between the predicted values and the experimental values for other strain rates is relatively good.
For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\text{MPa}$ and this shows an overall worse performance than the AR model.

@@

The Python program used for training the neural network was developed using the specialized Python library Tensorflow \cite{Abadi-2016}.
The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
The training data are those from the tests presented in section \ref{sec:ComTestResults} and composed of $21~000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
The learning is performed on the basis of $5~000$ epochs of the experimental data set.
Fourty minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GiB of Ram and an Intel 4-core i7-10510U processor allow obtaining the converged parameters of the ANN model.
Figure \ref{fig:ANN-6-conv} show the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$  during the training phase.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]
{Figures/Conv-ANN-6}
\caption{Convergence of the ANN model during the training phase.}
\label{fig:ANN-6-conv}
\end{figure}
As we can see on this figure, after $5~000$ epoch, we can consider that we have reached a stationary state of the model learning and that it is useless to continue the learning phase.

@@

As for the analytical models presented previously, Figure \ref{fig:CompExp-3-15-7-1-sigmoid} shows a comparison between the flow stresses predicted by the ANN model and the data measured during the hot compression test.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExp-3-15-7-1-sigmoid}
\caption{Comparison between the experimental and predicted flow stresses by the 3-15-7-1-sigmoid ANN model}
\label{fig:CompExp-3-15-7-1-sigmoid}
\end{figure}
The correlation between the experimental data and the ANN prediction is very good over the entire range of data and the predicted data can track the hardening and softening regions of the hot deformed material well.
For the ANN model, $\AARE=0.62~\%$ and $\RMSE=0.38~\text{MPa}$ which is excellent.
This model can be used to simulate the hot deformation of this type of alloy with much greater fidelity to the actual material behavior than the analytical models presented previously.

@@

A summary of the coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work is reported in Table \ref{tab:Errors}.
\begin{table}[h!]
\centering
\caption{Accuracy coefficients for all the analyzed models.}
\begin{tabular}{lcccccc}
	\hline
	Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
	$\AARE(\%)$         & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
	$\RMSE(\text{MPa})$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ \hline
\end{tabular}
\label{tab:Errors}
\end{table}
From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.The values of $\AARE$ and $\RMSE$ are globally 6 times lower than the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of hot forming of alloys \cite{Liang-2022}.

@@

For the validation of the interpolation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for ANN) are the 5 other, \ie $\mdot\varepsilon=[0.001, 0. 01, 0. 1, 2, 5]~\ps$.
All models were re-identified from the same experimental data on a data set corresponding to 5 strain rates and 5 temperatures.

Figure \ref{fig:CompInt} shows a comparison, for strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompInt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
\label{fig:CompInt}
\end{figure}
Table \ref{tab:IntVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=1~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of interpolation for all models with  $\mdot\varepsilon=1~\ps$}
\begin{tabular}{llcccccc}
	\hline
	Strain rate                      & Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
	                                 & $\RMSE(\text{MPa})$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \hline
	\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
	                                 & $\RMSE(\text{MPa})$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \hline
	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
	                                 & $\RMSE(\text{MPa})$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
\end{tabular}
\label{tab:IntVal}
\end{table}

@@

From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models.
Table \ref{tab:IntVal} shows the quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates (named id. $\mdot\varepsilon$), on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\text{MPa}$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.

@@

For validation of the models' ability to extrapolate, the omitted strain rate chosen is $\mdot\varepsilon=5~\ps$ and those used for identification are $\mdot\varepsilon=[0.001, 0. 01, 0. 1, 1, 2]~\ps$. The strain rate omitted in this analysis is therefore the highest value, which restricts the learning domain.

In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
\label{fig:CompExt}
\end{figure}
Table \ref{tab:ExtVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=5~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of extrapolation for all models with  $\mdot\varepsilon=5~\ps$}
\begin{tabular}{llcccccc}
	\hline
	Strain rate                      & Coefficients        &   JC    &   MZA   &   HS   &   AR   &   PTM   &  ANN   \\ \hline
	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$  & $0.61$ \\
	                                 & $\RMSE(\text{MPa})$ & $9.86$  & $16.26$ & $3.36$ & $2.32$ & $3.63$  & $0.32$ \\ \hline
	\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$ \\
	                                 & $\RMSE(\text{MPa})$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$ \\ \hline
	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$  & $1.09$ \\
	                                 & $\RMSE(\text{MPa})$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$ \\ \hline
\end{tabular}
\label{tab:ExtVal}
\end{table}

>>>>

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{\emph{i.e.}\@\xspace}
\DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\AARE}{\text{E}_\text{AAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

@@

The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
This method allows obtaining one after the other the 5 parameters in the order $A$, $B$, $n$, $C$ and $m$.
Thus, according to our experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
Thus, here, $B=21.816~\MPa$ and $n=0.0746$.
Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.3404$.
Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.7057$.
All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.

\begin{table}[h!]
\centering
\caption{Parameters' values of the Johnson-Cook flow law for the P20 steel.}
\begin{tabular}{ccccc}
	\hline
	$A~(\MPa)$ & $B~(\MPa)$ &   $n$    &   $C$    &   $m$    \\
	   $13.5143$     &     $21.816$     & $0.0746$ & $0.3404$ & $0.7057$ \\ \hline
\end{tabular}
\label{tab:JC}
\end{table}

@@

The accuracy and predictive ability of the models are usually assessed by certain coefficients such as the Mean Absolute Relative Error ($\AARE$) defined by Equation (\ref{eq:AARE}):
\begin{equation}
\AARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the Root Mean Square Error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value and $\sigma_i^p$ is the predicted value using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
For the JC model, $\AARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure in our case of study because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
Therefore, as a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model but simply establishes a good linearity correlation between the experiment and the prediction we avoided its use in our analysis.

@@

By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$.
The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively.
Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right),
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$.
Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$.
The parameters of MZA model are given in Table \ref{tab:MZA} while its prediction are plotted in Figure \ref{fig:CompExp-MZA-6}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{ccccccc}
	\hline
	  $C_1$   &   $C_2$   &         $C_3$          &         $C_4$          &  $C_5$   &         $C_6$         &   $n$    \\
	$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$ \\ \hline
\end{tabular}
\label{tab:MZA}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:CompExp-MZA-6}
\end{figure}
It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates.
The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation.
For the MZA model, $\AARE=21.20~\%$ and $\RMSE=19.57~\MPa$, this shows an overall worse performance than the JC model as reported in \cite{TizeMha-2022}.

@@

The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:CompExp-HS-6} where the dots represent the experimental values and the solid lines are the values predicted by the Hansel-Spittel flow law.
For the HS model, $\AARE=7.75~\%$ and $\RMSE=3.80~\MPa$.
It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1~\ps$.
This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate.
The DRX phenomena cannot be reproduced by this type of model.

@@

Figure \ref{fig:CompExp-AR-6} shows the comparison of the values predicted by the Arrhenius model and the experimental values.
The difference between the experimental and predicted values is small.
But for the strain rate $\mdot\varepsilon = 0.01~\ps$ and for the two low temperature values, the AR model is not able to predict the softening.
For the AR model, $\AARE=3.56~\%$ and $\RMSE=2.18~\MPa$.

@@

Comparison of predicted values of the PTM model and experimental values is shown in Figure \ref{fig:CompExp-PTM-6}.
The PTM model is suitable to describe the flow behavior of AISI P20 steel, but for the two strain rates $\mdot\varepsilon=0.01~\ps$ and $\mdot\varepsilon=0.1~\ps$ the prediction is not quite good.
The deviation between the predicted values and the experimental values for other strain rates is relatively good.
For the PTM model, $\AARE=4.79~\%$ and $\RMSE=4.59~\MPa$ and this shows an overall worse performance than the AR model.

@@

The Python program used for training the neural network was developed using the specialized Python library Tensorflow \cite{Abadi-2016}.
The Adaptive Moment Estimation (ADAM) optimizer \cite{Kingma-2015} was used for the training phase.
The training data are those from the tests presented in section \ref{sec:ComTestResults} and composed of $21~000$ quadruplets of ($\varepsilon^p$, $\mdot\varepsilon$, $T$, $\sigma^y$) values.
The learning is performed on the basis of $5~000$ epochs of the experimental data set.
Fourty minutes of training on a Dell XPS-13 7390 laptop running Ubuntu 22.04 LTS 64 bits with 16 GB of Ram and an Intel 4-core i7-10510U processor allow obtaining the converged parameters of the ANN model.
Figure \ref{fig:ANN-6-conv} show the evolution of the training error defined by the $\log_{10}$ of the $\RMSE$  during the training phase.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]
{Figures/Conv-ANN-6}
\caption{Convergence of the ANN model during the training phase.}
\label{fig:ANN-6-conv}
\end{figure}
As we can see on this figure, after $5~000$ epoch, we can consider that we have reached a stationary state of the model learning and that it is useless to continue the learning phase.

@@

As for the analytical models presented previously, Figure \ref{fig:CompExp-3-15-7-1-sigmoid} shows a comparison between the flow stresses predicted by the ANN model and the data measured during the hot compression test.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExp-3-15-7-1-sigmoid}
\caption{Comparison between the experimental and predicted flow stresses by the 3-15-7-1-sigmoid ANN model}
\label{fig:CompExp-3-15-7-1-sigmoid}
\end{figure}
The correlation between the experimental data and the ANN prediction is very good over the entire range of data and the predicted data can track the hardening and softening regions of the hot deformed material well.
For the ANN model, $\AARE=0.62~\%$ and $\RMSE=0.38~\MPa$ which is excellent.
This model can be used to simulate the hot deformation of this type of alloy with much greater fidelity to the actual material behavior than the analytical models presented previously.

@@

A summary of the coefficients for evaluating the high-temperature flow stress prediction capability of the AISI P20 alloy for all models presented in this work is reported in Table \ref{tab:Errors}.
\begin{table}[h!]
\centering
\caption{Accuracy coefficients for all the analyzed models.}
\begin{tabular}{lcccccc}
	\hline
	Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
	$\AARE(\%)$         & $14.05$ & $21.20$ & $7.75$ & $3.56$ & $4.79$ & $0.62$ \\
	$\RMSE(\MPa)$ & $12.00$ & $19.57$ & $3.80$ & $2.18$ & $4.59$ & $0.38$ \\ \hline
\end{tabular}
\label{tab:Errors}
\end{table}
From this table, we can see that the ANN model has a much better predictive capacity than all the analytical models presented previously.The values of $\AARE$ and $\RMSE$ are globally 6 times lower than the best of the analytical models, \ie the Arrhenius model, quoted as reference in the context of hot forming of alloys \cite{Liang-2022}.

@@

For the validation of the interpolation, the chosen omitted strain rate is $\mdot\varepsilon=1~\ps$ and those used for identification (or training for ANN) are the 5 other, \ie $\mdot\varepsilon=[0.001, 0.01, 0.1, 2, 5]~\ps$.
All models were re-identified from the same experimental data on a data set corresponding to 5 strain rates and 5 temperatures.

Figure \ref{fig:CompInt} shows a comparison, for strain rate $\mdot\varepsilon=1~\ps$, of the flow stresses $\sigma^y$ calculated by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompInt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
\label{fig:CompInt}
\end{figure}
Table \ref{tab:IntVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=1~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of interpolation for all models with  $\mdot\varepsilon=1~\ps$}
\begin{tabular}{llcccccc}
	\hline
	Strain rate                      & Coefficients        &   JC    &   MZA   &   HS   &   AR   &  PTM   &  ANN   \\ \hline
	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.79$ & $20.22$ & $8.57$ & $3.96$ & $5.10$ & $0.70$ \\
	                                 & $\RMSE(\MPa)$ & $11.83$ & $19.00$ & $3.97$ & $2.29$ & $4.73$ & $0.38$ \\ \hline
	\mr{2}{$\mdot\varepsilon=1~\ps$} & $\AARE(\%)$         & $14.87$ & $27.79$ & $3.74$ & $1.46$ & $3.16$ & $2.47$ \\
	                                 & $\RMSE(\MPa)$ & $12.02$ & $23.67$ & $3.10$ & $1.46$ & $2.65$ & $2.77$ \\ \hline
	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $14.42$ & $28.90$ & $7.55$ & $3.45$ & $4.90$ & $0.96$ \\
	                                 & $\RMSE(\MPa)$ & $11.86$ & $19.86$ & $3.84$ & $2.17$ & $4.45$ & $1.18$ \\ \hline
\end{tabular}
\label{tab:IntVal}
\end{table}

@@

From a general appearance point of view, the other 4 models, HS, AR, PTM and ANN, give globally similar results with a higher fidelity for the AR and ANN models compared to the other two models.
Table \ref{tab:IntVal} shows the quantitative comparison on $\AARE$ and $\RMSE$ for three different cases: on the 5 identified strain rates (named id. $\mdot\varepsilon$), on only the strain rate $\mdot\varepsilon=1~\ps$ and on all 6 strain rates for these 6 models.
It appears from this Table that if the two models AR and ANN give equivalent (and excellent) results concerning the values of $\AARE$ and $\RMSE$ for the strain rate $\mdot\varepsilon=1~\ps$, the ANN model gives globally a better result on the whole of the strain rates with values of $\AARE=0.96\%$ and $\RMSE=1.18~\MPa$ respectively, that is to say values approximately 2 to 3 times lower for the ANN model compared to the AR model.

@@

For validation of the models' ability to extrapolate, the omitted strain rate chosen is $\mdot\varepsilon=5~\ps$ and those used for identification are $\mdot\varepsilon=[0.001, 0.01, 0.1, 1, 2]~\ps$.
The strain rate omitted in this analysis is therefore the highest value, which restricts the learning domain.

In this new identification configuration, Figure \ref{fig:CompExt} shows a comparison, for strain rate $\mdot\varepsilon=5~\ps$, of the flow stresses $\sigma^y$ computed by the models (as a line) and the experimental results (as points) for the 5 analytical models and the neural network.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExt}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
\label{fig:CompExt}
\end{figure}
Table \ref{tab:ExtVal} shows the $\AARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the 6 strain rates (lines referred as: all) or only on the strain rate $\mdot\varepsilon=5~\ps$.
\begin{table}[h!]
\centering{}
\caption{Accuracy coefficients of extrapolation for all models with  $\mdot\varepsilon=5~\ps$}
\begin{tabular}{llcccccc}
	\hline
	Strain rate                      & Coefficients        &   JC    &   MZA   &   HS   &   AR   &   PTM   &  ANN   \\ \hline
	\mr{2}{id. $\mdot\varepsilon$}   & $\AARE(\%)$         & $13.09$ & $19.09$ & $7.30$ & $4.03$ & $4.34$  & $0.61$ \\
	                                 & $\RMSE(\MPa)$ & $9.86$  & $16.26$ & $3.36$ & $2.32$ & $3.63$  & $0.32$ \\ \hline
	\mr{2}{$\mdot\varepsilon=5~\ps$} & $\AARE(\%)$         & $20.16$ & $24.27$ & $7.73$ & $3.53$ & $11.46$ & $3.87$ \\
	                                 & $\RMSE(\MPa)$ & $20.73$ & $25.95$ & $7.83$ & $4.02$ & $12.91$ & $5.84$ \\ \hline
	\mr{2}{all $\mdot\varepsilon$}   & $\AARE(\%)$         & $15.12$ & $25.87$ & $7.12$ & $3.86$ & $5.34$  & $1.09$ \\
	                                 & $\RMSE(\MPa)$ & $12.36$ & $18.24$ & $4.43$ & $2.68$ & $6.23$  & $2.40$ \\ \hline
\end{tabular}
\label{tab:ExtVal}
\end{table}
